Regression for correlated variables : application in steel industry

### 2014-01-27 www/Rennes.tex
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@287 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Le modèle génératif}
On dispose de $X=(X^1,\dots,X^p)$ variables fortement corrélées pour expliquer une variable réponse $Y$.
On rend explicites les corrélations au sein de $X$ sous la forme d'une structure de sous-régressions linéaires $S=(p_2,I_2,p_1,I_1)$ définie ainsi :
	\begin{eqnarray}
		I_1&=&(I_1^1,\dots,I_1^{p}) \textrm{ avec}		\\
		I_1^j &=& \{i |Z_{i,j}=1 \} \textrm{ indices des covariables qui expliquent $X^j$} \\
		I_2&=&\{j |\sharp I_1^j>0 \}  \textrm{ indices des variables dépendantes} \\
		p_2&=& \sharp I_2 \\
		p_1&=&(p_1^1,\dots,p_1^{p_2}) \textrm{ avec }p_1^j=\sharp I_1^j 
	\end{eqnarray}
	On suppose $I_1\cap I_2=\emptyset$, $i.e.$ Les variables dépendantes dans $X$ n'en expliquent pas d'autres.

>>>>

\section{Le modèle génératif}
On dispose de $X=(X^1,\dots,X^p)$ variables fortement corrélées pour expliquer une variable réponse $Y$.
On rend explicites les corrélations au sein de $X$ sous la forme d'une structure de sous-régressions linéaires $S=(p_2,I_2,p_1,I_1)$ définie ainsi :
	\begin{eqnarray}
		I_1&=&\{I_1^1,\dots,I_1^{p}\} \textrm{ avec}		\\
		I_1^j &=&\{ \textrm{ indices des covariables qui expliquent $X^j$} \} \\ % \{i |Z_{i,j}=1 \} 
		I_2&=&\{j |\sharp I_1^j>0 \}  \textrm{ indices des variables dépendantes} \\
		p_2&=& \sharp I_2 \\
		p_1&=&(p_1^1,\dots,p_1^{p_2}) \textrm{ avec }p_1^j=\sharp I_1^j 
	\end{eqnarray}
%	Où $Z$ est la matrice d'adjacence du graphe qui définit les dépendances entres variables (SEM récursif).
	On suppose $I_1\cap I_2=\emptyset$, $i.e.$ Les variables dépendantes dans $X$ n'en expliquent pas d'autres.

### 2014-01-27 www/article9.tex
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@287 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

 	We then observe that the reduced model only uses the partition given by the structure (who is explained and who explains) but not the structure itself (how they interacts). We also notice that even if variables are highly correlated, each can have a specific effect ($\varepsilon_X$) on the response variable.

 	So in a second step we propose further usage of the structure, taking back correlated variables to estimate the residuals of the reduced model. This estimation is also a linear regression that can take profit from any variable selection method. The idea is to estimate the complete model under the constraint of the structure. It can be done with Constrained Least Squares \cite{amemiya1985advanced} or sequentially with classical OLS (non optimal but easier to use selection methods).

But to work, we need an explicit structure between the covariates. SEM are often used in social sciences and economy where a structure is supposed "by hand" but here we want to be able to find a structure without any a priori (possibility to include some known structure remains). Graphical LASSO \cite{friedman2008sparse} offers a method to obtain a structure based on the precision matrix (inverse of the variance-covariance matrix). It consists in a selection in the precision matrix, setting some covariances to zero. But the resulting matrix is symmetric and we need an oriented graph for our SEM. So we developped an MCMC algorithm to find it (R package CorReg on Rforge). However, Graphical LASSO can be used in the initialization step of our MCMC. This structure is based on gaussian mixture models to fit better real datasets and to allow identifiability of the structure in terms of complexity (number of parameters).

 	~\\

>>>>

% 	We then observe that the reduced model only uses the partition given by the structure (who is explained and who explains) but not the structure itself (how they interacts). We also notice that even if variables are highly correlated, each can have a specific effect ($\varepsilon_X$) on the response variable.
% 	
% 	So in a second step we propose further usage of the structure, taking back correlated variables to estimate the residuals of the reduced model. This estimation is also a linear regression that can take profit from any variable selection method. The idea is to estimate the complete model under the constraint of the structure. It can be done with Constrained Least Squares \cite{amemiya1985advanced} or sequentially with classical OLS (non optimal but easier to use selection methods).
% 	
%

But to work, we need an explicit structure between the covariates. SEM are often used in social sciences and economy where a structure is supposed "by hand" but here we want to be able to find a structure without any a priori (possibility to include some known structure remains). Graphical LASSO \cite{friedman2008sparse} offers a method to obtain a structure based on the precision matrix (inverse of the variance-covariance matrix). It consists in a selection in the precision matrix, setting some covariances to zero. But the resulting matrix is symmetric and we need an oriented graph for our SEM. So we developped an MCMC algorithm to find it (R package CorReg on Rforge). However, Graphical LASSO can be used in the initialization step of our MCMC. This structure is based on gaussian mixture models to fit better real datasets and to allow identifiability of the structure in terms of complexity (number of parameters).
 	\\
